Research on information extraction (IE) from visually rich documents has produced a broad ecosystem of datasets and models. However, much of the public evaluation landscape emphasizes either short documents (e.g., forms) or key-value extraction, leaving long-list entity extraction underexplored.

\subsection{Document IE benchmarks}
Early and widely used benchmarks such as FUNSD~\cite{jaume2019funsd} focus on form understanding in noisy scans. Receipt datasets such as SROIE~\cite{huang2021sroie} and CORD~\cite{park2019cord} emphasize OCR, key fields, and relatively short item structures in narrow document types. These benchmarks are valuable, but typically contain relatively short documents and do not directly stress long lists of repeated entities.

DocILE~\cite{simsa2023docile} broadens the scope to business documents and includes line-item recognition, which is closer in spirit to long-list extraction. Document question answering benchmarks such as DocVQA~\cite{mathew2021docvqa} and MP-DocVQA~\cite{tito2022mpdocvqa} show that reasoning over document pages, especially multi-page documents, remains difficult; however, they evaluate question answering rather than recovery of full repeated record sets. VRDU~\cite{wang2023vrdu} further argues that hierarchical and repeated fields (e.g., invoice line items) remain difficult for LLM-based extraction. More recent parsing-oriented benchmarks such as OmniDocBench~\cite{ouyang2024omnidocbench} expand coverage across diverse PDF document types and evaluation tasks, but their primary emphasis is broad document parsing rather than repeated-entity extraction under long-list stressors. Our benchmark complements these efforts by focusing specifically on list length, repeated entity boundaries, and a targeted taxonomy of long-list failure modes.

\subsection{Document understanding models}
Layout-aware pretraining approaches such as LayoutLM~\cite{xu2020layoutlm} and LayoutLMv3~\cite{huang2022layoutlmv3} jointly model textual content, document structure, and visual signals, yielding strong performance on a range of document understanding tasks. In parallel, OCR-free approaches such as Donut~\cite{kim2022donut} avoid explicit OCR by directly generating structured outputs from document images, mitigating OCR error propagation at the cost of specialized training. More recent layout-aware LLM and MLLM systems such as DocLLM~\cite{wang2024docllm} and DocLayLLM~\cite{liao2024doclayllm} push document understanding toward instruction-following, generative extraction, and richer multimodal reasoning.

In contrast, our work is model-agnostic: we provide paired PDF, OCR text, and ground truth, enabling evaluation of OCR-based pipelines, OCR-free models, and LLM-based extraction. Our primary goal is to support reproducible measurement of long-list extraction robustness under realistic layout artifacts.
