We evaluate systems on the task of extracting a list of incident records from the OCR text of each PDF. The benchmark provides both the OCR text and a structured JSON ground truth for each document.

\subsection{OCR}
All PDFs are converted to Markdown using a Gemini vision model. Each page is rendered to an image and converted to text with a system prompt that emphasizes preserving layout, spacing, and tables. In particular, tables are emitted in a CSV-like form inside Markdown, and the output is concatenated across pages.

\subsection{LLM extraction regimes}
We compare two zero-shot extraction regimes on the same extraction task and target schema. In both cases, the model is asked to return a JSON list of incident objects conforming to the full incident schema, and where supported we request native structured outputs to reduce formatting errors.

\paragraph{Full-context one-shot extraction.}
The entire OCR text of a document is provided to the model in a single call. No chunking or post-hoc merge is performed. This regime directly measures whether an LLM can recover all incidents from one long prompt. When the model response is truncated, only the complete incidents that can be salvaged from the partial JSON are retained before scoring.

\paragraph{Auto-chunked extraction.}
Our current \texttt{longlistbench} harness detects long OCR inputs, measures OCR length with the Gemini token-count API, and splits long inputs into fixed token-budget chunks. Each chunk is extracted independently, and the resulting incident lists are concatenated before scoring. The current Gemini implementation uses a maximum OCR input budget of 12{,}000 tokens per chunk.

To ensure schema conformance, model outputs are validated and normalized against a Pydantic schema before scoring (see \hyperref[sec:appendix-schemas]{Appendix~A} for full schema definitions and scoring rules). Predictions and aggregate reports are stored as machine-readable JSON (with an additional Markdown summary for convenience).

\subsection{Report regeneration and validation}
To support reproducible analysis, the harness can regenerate summary reports offline from saved prediction files and optionally reuse extraction-time values from a previous report. A companion checker recomputes metrics from the saved predictions and the golden data, and flags schema violations or report inconsistencies.

\subsection{Field-level matching and metrics}
For scoring we use the incident number as the record identifier. Incident numbers are normalized by stripping common prefixes (e.g., \texttt{\#}, \texttt{Incident \#}). Let $G$ be the list of ground-truth records and $P$ be the list of predicted records. We compute micro precision/recall/F1 over field-value pairs, after canonicalizing each incident under the schema.

Canonicalization strips whitespace from strings, maps empty optional strings to null, sorts claimant lists, and rounds monetary values in nested financial breakdowns to two decimal places. Our primary reported metric is corpus-level micro precision/recall/F1 over the full benchmark (or a full tier/format slice), obtained by aggregating field-value matches across all documents. This weighting favors incident volume rather than treating a 10-row document and a 500-row document equally. For completeness, we also report document-macro summaries obtained by averaging per-document scores.

For each incident, we flatten its fields into a multiset of canonicalized triples (\path{incident_id}, \path{field_path}, \path{value}) (including nested financial breakdown fields). We then define:
\begin{align}
\mathrm{found} &= |\mathcal{F}(G) \cap \mathcal{F}(P)|,\\
\mathrm{recall} &= \frac{\mathrm{found}}{|\mathcal{F}(G)|},\\
\mathrm{precision} &= \frac{\mathrm{found}}{|\mathcal{F}(P)|},\\
\mathrm{F1} &= \frac{2\,\mathrm{precision}\,\mathrm{recall}}{\mathrm{precision}+\mathrm{recall}},
\end{align}
where $\mathcal{F}(\cdot)$ denotes the multiset of flattened field-value pairs across incidents. We additionally report missing and extra incident identifiers and count exact record matches for incidents whose canonicalized objects match exactly.
%
