LongListBench targets a persistent gap in document understanding evaluation: extracting long lists of repeated entities from semi-structured business documents under complex layouts and OCR noise. We presented a benchmark construction pipeline that produces paired rendered artifacts, paired clean and OCR transcripts, and JSON ground truth while systematically injecting common long-list failure modes.

\subsection{Summary}
Our main contributions are:
\begin{itemize}
    \item A reproducible benchmark generation pipeline for semi-structured documents with long incident lists spanning two formats and four difficulty tiers.
    \item A taxonomy of seven problem types that frequently break long-list extraction systems, including duplicates, page breaks, multi-row entities, multi-column layout, and merged cells.
    \item An evaluation harness that supports direct clean-vs-OCR comparisons in addition to OCR-condition baseline results.
\end{itemize}

\subsection{Practical takeaways}
We intend LongListBench to be useful as a measurement tool for both research and engineering workflows. Two practical takeaways are worth emphasizing. First, OCR should be treated as a controlled condition rather than the entire task definition: comparing `canonical` and `ocr` transcript conditions lets practitioners estimate OCR penalty without conflating it with downstream extraction difficulty. Second, even with schema-conformant structured outputs, the extraction regime matters substantially: the local full-context one-shot Gemini baseline reaches only 5.9\% field-level micro $F_1$ on the OCR extreme tier, while the simplified local chunked baseline reaches 81.7\% on the same snapshot (Table~\ref{tab:two-regimes}). This gap indicates that chunking is an important mitigation for long documents, but not a complete solution to layout-sensitive extraction errors, especially for long detailed documents.

\subsection{Recommended reporting}
For comparability across papers and systems, we recommend that LongListBench results report (i) transcript condition (`canonical` or `ocr`), (ii) corpus-level weighted field-level precision/recall/F1, (iii) document-macro summaries as a secondary view, (iv) OCR penalty when both transcript conditions are evaluated, and (v) the extraction protocol used for long documents (e.g., one-shot vs chunking and the chunk token budget). The extreme tier, in particular, is intended to stress scaling behavior: methods that succeed on short lists may fail due to context limits, brittle segmentation, or accumulated small errors across hundreds of records.

\subsection{Future Work}
We view the benchmark as a foundation for studying scalable, layout-robust extraction. Immediate next steps include improved handling of duplicates and merged cells, and evaluation of methods that can reliably extract hundreds of incidents in a single document (Section~\ref{sec:limitations}).
